A comparison of different methods for calculating tangent-stiffness matrices in a massively parallel computational peridynamics code.

### 2014-02-27 response/response.tex

{\color{red}
  \begin{itemize}
    \item 
      The added subsection 'Convergence and displacement accuracy studies'
      includes convergence rate and displacement accuracy studies similar to
      those shown in 'Working examples ...', but with the models and tools of
      the main study. This subsection provides an example of interest. 
  \item 
      To summarize, these studies are done in \emph{Peridigm} using the most refined mesh
      from the 'serial' test runs from the original manuscript. Measured was the performance of the methods in terms of speed
      (convergence rate) and accuracy (displacement accuracy).  Iteration speed
      was reported in the original manuscript.
  \item
      It was determined that the accuracy of CS over FD resulted in no appreciable
      advantage in terms of displacement accuracy or convergence rate for the problems
      solved in this study. 
    \item
      Additional comment on the significance of the accuracy of the Jacobian
      to Newton's method is included in the subsections 'For further studies of
      Jacobian accuracy in Newton's method', 'Grain of salt for speed results'
      and 'Remarks'. 
  \item 
      To summarize, Newton's method is insensitive to the accuracy differences
      shown by the methods, for the problems shown, when the methods are not
      deliberately misused with inappropriate step sizes. For completeness,
      formulas describing a relationship between Jacobian accuracy and
      convergence rate order are included. 
  \item
      It is the authors' opinion that the above revisions offer the discussion of relative problem solving
      performance of the methods that the reviewer has requested, including consideration
      of speed and accuracy in solving real, non-linear problems.
  \end{itemize}}

  \subsection*{Smaller issues}
  \begin{enumerate}
  \item
	1. Pg. 2: In line 14, explain what does the term “algorithmically consistent” mean.

{\color{red}
  \begin{itemize}
     \item
      A brief definition for the convenience of the reader was added in the manuscript. But, algorithmically consistent is a fairly common term in plasticity/mechanics. This same meaning is used for 'consistent' refering to 'tangent matrices' in \cite[perez2012consistent, perez2010]. It means consistent with integrating the plasticity model under the Khun-Tucker constraints. Integrating the plasticity model means, given a strain increment, determining a stress that does not exceed the yield stress, and by doing so computing a linear slope, called a consistent tangent modulus, that relates the strain increment to a correct stress increment. An alogorithmically consistent tangent stiffness matrix is then one that uses the consistent tangent modulii, making it a more accurate approximation of the stiffness of the system. 
  \end{itemize}}

  \item
	2. Pg. 2: In line 36, what do you mean by “discrimination”?

{\color{red}  
\begin{itemize}
     \item
      The word, 'discrimination' has been removed from the manuscript. 'Discrimination' was meant to mean 'measuring differences and making judgements on relative usefulness'. Since this meaning is probably understood from the word 'comparison' alone, the word 'discrimination' has been removed from the manuscript for clarity.
  \end{itemize}}

` \item	
	3. Pg. 2: In line 37, explain what do you mean by “in-situ instrumentation”.

{\color{red}  
\begin{itemize}
     \item
      The words, 'in-situ' have been removed from the manuscript. 'In-situ' was meant to suggest that timing measurements were taken from within and by the program being analyzed itself, rather than by an external program, but it has been removed for clarity.
  \end{itemize}}

  \item 
	4. Pg. 3: In lines 19-29, specify the sections where each part of the manuscript is
included.
{\color{red}  
\begin{itemize}
     \item
      The correction is made in the manunscript.
  \end{itemize}}

### 2014-02-27 jacobian_calc_CMAME.tex
addressed smaller issues 1 through 4

In order to maintain the quadratic convergence properties of Newton's method in
quasi-static nonlinear analysis of solid structures it is crucial to obtain
accurate, algorithmically consistent tangent-stiffness matrices. A goal of the
study described in this paper was to establish the suitability of an
under-explored method for numerical computation of tangent-stiffness operators,
referred to as ``complex-step'', and compare the \note[Michael]{re: I.1}
\remove[Michael]{new} method with other techniques for numerical derivative
calculation: automatic differentiation, forward finite-difference, and central
finite-difference. The complex-step method was \note[Michael]{re: I.1, could
suggest claim of novelty} \remove[Michael]{newly} implemented in a massively
parallel computational peridynamics code for the purpose of this comparison.
The methods were compared through in situ profiling of the code for accuracy,
speed, efficiency, and parallel scalability. The research provides data that
can serve as practical guide for code developers and analysts faced with
choosing which method best suits the needs of their application code.
Additionally, motivated by the reproducible research movement, all the of the
code, examples, and workflow to regenerate the data and figures in this paper
are provided as open source.

@@

A goal of this study was to develop and evaluate a \note[Michael]{re: I.1}
\change[Michael]{new}{relatively underexplored}, accurate, and practical method
for calculating tangent-stiffness matrices against established methods.  This
new method is based on a complex number Taylor series expansion and referred to
as CTSE or the ``complex-step'' method.  The distinction of ``accurate'' is
defined by comparison of the \note[Michael]{re: I.1}\remove[Michael]{new} method to popular finite differencing
techniques used for computing tangent-stiffness matrices and with the exact to
machine precision algorithmically consistent derivatives computed with
\emph{automatic differentiation}.

Comparative data regarding the accuracy and compute cycle timing for the
complex step, finite-difference, central-difference, and automatic
differentiation methods are included to aide developers and analysts in
computational mechanics code design who are faced with implementing a general
method for tangent stiffness matrix calculation.  A comparison and
discrimination of the methods was achieved through in-situ instrumentation of a
massively parallel computational mechanics code.

@@

The aim of this paper is not only to \note[Michael]{re: I.1}\change[Michael]{introduce the new}{study the} complex-step method \change[Michael]{in
the context of}{of} evaluating tangent-stiffness matrices, but to serve as a review
for other differentiation techniques useful for solving non-linear systems with
Newton's method. After presenting background information on the underlying
methods to be discussed, presented in this paper are: A) a description of
tangent-stiffness matrices, B) detailed directions for producing
tangent-stiffness matrices with each of the methods identified above, C) a
description and justification of the \note[Michael]{re: I.1}\remove[Michael]{new}complex-step method for calculating
tangent-stiffness matrices, D) a description of implementing complex-step in
the \emph{Peridigm} software, E) a description of the quantities-of-interest
used to rank the methods, F) a presentation and analysis of the results of the
comparative study, and G) conclusions and thoughts on potential future work.
Finally, in the interest of replicable research, the reader is referred to the
corresponding author's website for \emph{Peridigm} C++ source-code and data
necessary to reproduce the results presented here. Additionally, included on
the website is an example serial C++ library with classes for solving
non-linear systems using the techniques discussed here, as well as two
validation and verification example problems which show how to use the library.
The purpose of the serial C++ library is to demonstrate in a less complex
manner than in the \emph{Peridigm} code how one would use
automatic-differentiation or complex-step to better encourage their use and
discussion. This open source resource will be referred to as the \emph{paper
repository} in what follows.

@@

\subsection{Tangent-stiffness}

In solid and structural computational mechanics the tangent-stiffness matrix is
a linearization operator that describes the stiffness of a system in response
to small displacements imposed upon the current configuration of the system.
Mathematically speaking, the tangent-stiffness represents the gradient of a
high-dimensional energy surface that ``points'' in the minimum direction. While
the terminology of solid mechanics is used here, it's important to note that
these operators appear in other physical settings and are known by other names,
e.g. a \emph{transmissibility matrix} in the context of a Poisson problem or,
more generally, a \emph{Jacobian matrix} in mathematical optimization.

@@

\section{Description of analysis tools and approach.} 
%
\subsection{\emph{Peridigm} and peridynamics.}
%
Comparisons of the different tangent-stiffness calculation techniques were
carried out through code-development and \emph{in situ} instrumentation of the
computational peridynamics code \emph{Peridigm} \cite{peridigm}.
\emph{Peridigm} is distributed by Sandia National Laboratories as its primary
open-source computational peridynamics code. It is a massively parallel
simulation code for implicit and explicit multi-physics simulations primarily
used for solid mechanics and material failure. \emph{Peridigm} is a C++ code
utilizing agile software components from Sandia's  \emph{Trilinos} project
\cite{trilinos}. It's important to note that there is no specialization of the
tangent-stiffness calculation methods described previously to this particular
code or more generally to a computational peridynamics approach and the
analysis carried out in this study should provide insight into the speed and
accuracy of these methods when implemented into other computational mechanics
analysis tools as well.  \emph{Peridigm} was chosen primarily because the FD,
CD, and AD methods for tangent-stiffness calculation where already implemented
in the code, leaving only the CS method for development. Also, because
peridynamics is a nonlocal theory, the tangent-stiffness matrices have a much
higher bandwidth (i.e. less sparsity) than traditional finite-element
tangent-stiffness computations and the time required to construct the
tangent-stiffness is a majority of the total computation time in any
quasi-static or implicit dynamics analysis; therefore, the \emph{Peridigm}
development team has an interest in profiling the performance of the
tangent-stiffness computation methods.

@@

\subsubsection{Implementing the complex-step method in Peridigm} 
%
The CS method was implemented in \emph{Perdigm} in a manner that follows
closely the implementation of the FD technique.  However, because of
\emph{Peridigm}'s reliance on \emph{Trilinos} and specifically the
\emph{Epetra} package, special steps had to be followed to allow the use of
complex number data types.  This is because \emph{Epetra} vectors, which can be
thought of as distributed memory parallel cousins to standard C++
\change[Michael]{STL}{Standard Template Library} vectors, are hard coded to be
of type {\tt double} and can not be simply be declared as having a complex data
type. \note[Michael]{re: I.3}\add[Michael]{For the reader's convenience,
    \emph{Epetra} vectors and STL vectors are what are known as 'container
    classes', whose purpose in object oriented computer programming is to
    automate the creation, accessing, modification and destruction of the
    underlying contained data. Templated container classes allow for user
    choice in what properties that underlying data exihibits.  For example, in
    this work, complex arithmetic cannot be performed on the data contained
    within an \emph{Epetra} vector because that data, of type {\tt double} does
    not have the property of following the rules of complex arithmetic. The
    reason the non-templated \emph{Epetra} vector could not be dispensed with
    for the purposes of this work is because the \emph{Epetra} vector was
tightly integrated with \emph{Peridigm's} parallel communication strategy and
linear algebra code.} Program methods that were used in the course of applying
the FD method were copied, renamed and re-written to follow the CS formula.
Because of restrictions imposed by the container class being used, this
involved changing the data type of intermediate variables which were locally
scoped, and dynamically casting persistent memory variables to complex data
types where necessary. \note[Michael]{re: I.3}\add[Michael]{For the reader's
convenience, 'locally scoped' in the C++ programming language refers to
data which is created within a context more specific than the context of
the entire program, or 'translation unit'.  Most data created this way is
destroyed when that specific context is left. The topic of contexts in C++
is very broad, so for the purposes of this work context refers to a program
method or function that begins, concludes and yields a result, also
destroying locally scoped data. Dynamic casting for the purposes of this
work refers to copying the value of data contained within an \emph{Epetra}
vector into locally scoped data that has the property of following the rules of
complex arithmetic, where a mapping called 'type casting' allows the
translation of data between different types.} No attempt was made to ``tune''
the CS code in any way for performance. The algorithm  was implemented in such
as way that it was in one-to-one correspondence with the FD and CD methods;
however, it must be noted that the overhead associated with the dynamic casts
in the CS method likely hurts its overall performance and this issue could be
alleviated by using the next generation of templated \emph{TPetra} vectors
available in \emph{Trilinos} that are capable of taking an explicit
instantiation of any data type including {\tt complex}. \note[Michael]{re:
I.3}\add[Michael]{For the purposes of this work, an explicit instantiation
refers to requesting the creation of an object, or instance, of a templated
class or container class that holds data which has the property of
following desired mathematic or logic rules.} The version of \emph{Peridigm}
modified to implement CS can be found in the paper repository.

@@

\section{Results and Discussion}
%
Table~\ref{tab:results} shows the compute core count, number of nonzero tangent-stiffness (TS) non-zero matrix elements, load step average calculation time and load step average accuracy. The units for accuracy are derived equation~(\ref{eqn:accuracy}) and the units used to define bulk material properties, mentioned in Section~\ref{tcs}.
%
\begin{table*}[!ht]    
  \scriptsize
  \centering
        \caption{Averaged Results, Each Test} \label{tab:results}   
       \begin{tabular}{c c c c c c c c c}
         \toprule
         Cores & TS Elements & \multicolumn{4}{c}{Calculation Time ($\si{\second}$)} & \multicolumn{3}{c}{Accuracy Difference ($\si{\mega\pascal}$)} \\ 
         & $\times 10^6$ & CS & CD & FD & AD & CS & CD & FD \\
        \midrule
        1 & $\num{1.99}$  & 3.5 & 2.7 & 1.7 & 1.6 & $\num{1.92E-10}$ & $\num{1.21E-4}$ & .137 \\
        1 & $\num{4.25}$  & 6.2& 4.9& 3.2& 2.9 & $\num{2.28E-10}$& $\num{9.94E-4}$ & .148 \\
        1 & $\num{7.79}$  & 11.2& 8.9& 5.7& 5.2 & $\num{2.38E-10}$& $\num{1.59E-4}$ & .145\\
        1 & $\num{15.4}$  & 26.7& 21.0& 13.4& 12.2 & $\num{2.33E-10}$ & $\num{4.61E-4}$ & .12 \\
        1 & $\num{20.0}$  & 28.1& 22.2& 14.4& 13.1 & $\num{2.76E-10}$ & $\num{1.05E-3}$ & .145 \\
        1 & $\num{31.4}$  & 47.6& 37.7& 24.2& 21.9 & $\num{2.64E-10}$ & $\num{1.65E-3}$ & .133 \\
        1 & $\num{40.1}$  & 55.6& 44.1& 28.4& 25.9 & $\num{3.03E-10}$ & $\num{1.92E-3}$ & .148 \\
        1 & $\num{83.9}$  & 138.9& 109.6& 70.2& 64.0 & $\num{3.63E-10}$ & $\num{1.64E-3}$ & .123 \\
        1 & $\num{165.0}$  & 277.3& 218.1& 139.4& 126.5 & $\num{3.26E-10}$ & $\num{2.18E-3}$ & .128 \\
        32 & $\num{1670}$  & 336.1& 277.7& 200.6& 233.1 & $\num{6.21E-10}$ & $\num{1.52E-2}$ & .176 \\
        64 & $\num{1670}$  & 169.9& 140.7& 102.0& 119.7 & $\num{6.20E-10}$ & $\num{1.50E-2}$ & .177 \\
        96 & $\num{1670}$  & 114.7& 95.0& 69.1 & 79.7 & $\num{6.18E-10}$ & $\num{1.50E-2}$ & .177 \\
        128 & $\num{1670}$  & 86.4& 71.8& 52.4 &58.8 & $\num{6.16E-10}$ & $\num{1.47E-2}$ & .177 \\
        \bottomrule
    \end{tabular}
\end{table*}

@@

\section{Conclusions}
%
\subsection{For further studies of Jacobian accuracy in Newton's method}
\label{subsec:FurtherStudies}
The question is raised; what is the significance of Jacobian estimation
accuracy to the convergence of Newton's method?  The per-iteration and even
convergence studies shown here indicate the effect of Jacobian accuracy for
only a single datum, a very accurate Jacobian estimate, while the validation
problem indicates the effect of using a grossly inaccurate Jacobian. The results here show that
for very small Jacobian estimate inaccuracies, convergence rate is not
affected, while for grossly inaccurate Jacobians Newton's method fails. 
Additional confounding factors include that a Jacobian is only first
order approximation of an often curved energy surface and that a non-naive implementation of Newton's
method includes a line search phase that helps in choosing an optimal iterate given a Jacobian.
Is it worthwhile then to investigate the effect of using moderately inaccurate Jacobians, 
produced deliberately or otherwise, on the convergence rate of Newton's method?

>>>>

In order to maintain the quadratic convergence properties of Newton's method in
quasi-static nonlinear analysis of solid structures it is crucial to obtain
accurate, algorithmically consistent tangent-stiffness matrices. A goal of the
study described in this paper was to establish the suitability of an
under-explored method for numerical computation of tangent-stiffness operators,
referred to as ``complex-step'', and compare the \note[Michael]{re: I.1}
\remove[Michael]{new} method with other techniques for numerical derivative
calculation: automatic differentiation, forward finite-difference, and central
finite-difference. The complex-step method was \note[Michael]{re: I.1, could
suggest claim of novelty} \remove[Michael]{newly} implemented in a massively
parallel computational peridynamics code for the purpose of this comparison.
The methods were compared through profiling of the code for accuracy,
speed, efficiency, and parallel scalability. The research provides data that
can serve as practical guide for code developers and analysts faced with
choosing which method best suits the needs of their application code.
Additionally, motivated by the reproducible research movement, all the of the
code, examples, and workflow to regenerate the data and figures in this paper
are provided as open source.

@@

A goal of this study was to develop and evaluate a \note[Michael]{re: I.1}
\change[Michael]{new}{relatively underexplored}, accurate, and practical method
for calculating tangent-stiffness matrices against established methods.  This
new method is based on a complex number Taylor series expansion and referred to
as CTSE or the ``complex-step'' method.  The distinction of ``accurate'' is
defined by comparison of the \note[Michael]{re: I.1}\remove[Michael]{new}
method to popular finite differencing techniques used for computing
tangent-stiffness matrices and with the exact to machine precision
algorithmically consistent derivatives computed with \emph{automatic
differentiation}. For the reader's convenience, from plasticity theory, the algorithmic consistency of
the tangent-stiffness matrix refers to consistency with the integration of a
plasticity model under the Khun-Tucker constraints or similar where the tangent-stiffness matrix is
computed using the elastoplastic modulii that are determined from the integration \cite{simo1998}.

Comparative data regarding the accuracy and compute cycle timing for the
complex step, finite-difference, central-difference, and automatic
differentiation methods are included to aide developers and analysts in
computational mechanics code design who are faced with implementing a general
method for tangent stiffness matrix calculation.  A comparison of the methods was achieved through instrumentation of a
massively parallel computational mechanics code.

@@

The aim of this paper is not only to \note[Michael]{re: I.1}\change[Michael]{introduce the new}{study the} complex-step method \change[Michael]{in
the context of}{of} evaluating tangent-stiffness matrices, but to serve as a review
for other differentiation techniques useful for solving non-linear systems with
Newton's method. After presenting background information on the underlying
methods to be discussed, presented in this paper are: In subsection~\ref{subsec:TS} a description of
tangent-stiffness matrices, detailed directions for producing
tangent-stiffness matrices with each of the methods identified above, and a
description and justification of the \note[Michael]{re: I.1}\remove[Michael]{new}complex-step method for calculating
tangent-stiffness matrices, in sub-subsection~\ref{subsubsec:Impl} a description of implementing complex-step in
the \emph{Peridigm} software, in section~\ref{JGAM} a description of the quantities-of-interest
used to rank the methods, in section~\ref{sec:Res} a presentation and analysis of the results of the
comparative study, and in section~\ref{sec:Conc} conclusions and thoughts on potential future work.
Finally, in the interest of replicable research, the reader is referred to the
corresponding author's website for \emph{Peridigm} C++ source-code and data
necessary to reproduce the results presented here. Additionally, included on
the website is an example serial C++ library with classes for solving
non-linear systems using the techniques discussed here, as well as two
validation and verification example problems which show how to use the library.
The purpose of the serial C++ library is to demonstrate in a less complex
manner than in the \emph{Peridigm} code how one would use
automatic-differentiation or complex-step to better encourage their use and
discussion. This open source resource will be referred to as the \emph{paper
repository} in what follows.

@@

\subsection{Tangent-stiffness} 
\label{subsec:TS}
In solid and structural computational mechanics the tangent-stiffness matrix is
a linearization operator that describes the stiffness of a system in response
to small displacements imposed upon the current configuration of the system.
Mathematically speaking, the tangent-stiffness represents the gradient of a
high-dimensional energy surface that ``points'' in the minimum direction. While
the terminology of solid mechanics is used here, it's important to note that
these operators appear in other physical settings and are known by other names,
e.g. a \emph{transmissibility matrix} in the context of a Poisson problem or,
more generally, a \emph{Jacobian matrix} in mathematical optimization.

@@

\section{Description of analysis tools and approach.} 
%
\subsection{\emph{Peridigm} and peridynamics.}
\label{subsec:PaP}
%
Comparisons of the different tangent-stiffness calculation techniques were
carried out through code-development and instrumentation of the
computational peridynamics code \emph{Peridigm} \cite{peridigm}.
\emph{Peridigm} is distributed by Sandia National Laboratories as its primary
open-source computational peridynamics code. It is a massively parallel
simulation code for implicit and explicit multi-physics simulations primarily
used for solid mechanics and material failure. \emph{Peridigm} is a C++ code
utilizing agile software components from Sandia's  \emph{Trilinos} project
\cite{trilinos}. It's important to note that there is no specialization of the
tangent-stiffness calculation methods described previously to this particular
code or more generally to a computational peridynamics approach and the
analysis carried out in this study should provide insight into the speed and
accuracy of these methods when implemented into other computational mechanics
analysis tools as well.  \emph{Peridigm} was chosen primarily because the FD,
CD, and AD methods for tangent-stiffness calculation where already implemented
in the code, leaving only the CS method for development. Also, because
peridynamics is a nonlocal theory, the tangent-stiffness matrices have a much
higher bandwidth (i.e. less sparsity) than traditional finite-element
tangent-stiffness computations and the time required to construct the
tangent-stiffness is a majority of the total computation time in any
quasi-static or implicit dynamics analysis; therefore, the \emph{Peridigm}
development team has an interest in profiling the performance of the
tangent-stiffness computation methods.

@@

\subsubsection{Implementing the complex-step method in Peridigm} 
\label{subsubsec:Impl}
%
The CS method was implemented in \emph{Perdigm} in a manner that follows
closely the implementation of the FD technique.  However, because of
\emph{Peridigm}'s reliance on \emph{Trilinos} and specifically the
\emph{Epetra} package, special steps had to be followed to allow the use of
complex number data types.  This is because \emph{Epetra} vectors, which can be
thought of as distributed memory parallel cousins to standard C++
\change[Michael]{STL}{Standard Template Library} vectors, are hard coded to be
of type {\tt double} and can not be simply be declared as having a complex data
type. \note[Michael]{re: I.3}\add[Michael]{For the reader's convenience,
    \emph{Epetra} vectors and STL vectors are what are known as 'container
    classes', whose purpose in object oriented computer programming is to
    automate the creation, accessing, modification and destruction of the
    underlying contained data. Templated container classes allow for user
    choice in what properties that underlying data exihibits.  For example, in
    this work, complex arithmetic cannot be performed on the data contained
    within an \emph{Epetra} vector because that data, of type {\tt double} does
    not have the property of following the rules of complex arithmetic. The
    reason the non-templated \emph{Epetra} vector could not be dispensed with
    for the purposes of this work is because the \emph{Epetra} vector was
tightly integrated with \emph{Peridigm's} parallel communication strategy and
linear algebra code.} Program methods that were used in the course of applying
the FD method were copied, renamed and re-written to follow the CS formula.
Because of restrictions imposed by the container class being used, this
involved changing the data type of intermediate variables which were locally
scoped, and dynamically casting persistent memory variables to complex data
types where necessary. \note[Michael]{re: I.3}\add[Michael]{For the reader's
convenience, 'locally scoped' in the C++ programming language refers to
data which is created within a context more specific than the context of
the entire program, or 'translation unit'.  Most data created this way is
destroyed when that specific context is left. The topic of contexts in C++
is very broad, so for the purposes of this work context refers to a program
method or function that begins, concludes and yields a result, also
destroying locally scoped data. Dynamic casting for the purposes of this
work refers to copying the value of data contained within an \emph{Epetra}
vector into locally scoped data that has the property of following the rules of
complex arithmetic, where a mapping called 'type casting' allows the
translation of data between different types.} No attempt was made to ``tune''
the CS code in any way for performance. The algorithm  was implemented in such
as way that it was in one-to-one correspondence with the FD and CD methods;
however, it must be noted that the overhead associated with the dynamic casts
in the CS method likely hurts its overall performance and this issue could be
alleviated by using the next generation of templated \emph{TPetra} vectors
available in \emph{Trilinos} that are capable of taking an explicit
instantiation of any data type including {\tt complex}. \note[Michael]{re:
I.3}\add[Michael]{For the purposes of this work, an explicit instantiation
refers to requesting the creation of an object, or instance, of a templated
class or container class that holds data which has the property of
following desired mathematic or logic rules.} The version of \emph{Peridigm}
modified to implement CS can be found in the paper repository.

@@

\section{Results and Discussion}
\label{sec:Res}
%
Table~\ref{tab:results} shows the compute core count, number of nonzero tangent-stiffness (TS) non-zero matrix elements, load step average calculation time and load step average accuracy. The units for accuracy are derived equation~(\ref{eqn:accuracy}) and the units used to define bulk material properties, mentioned in Section~\ref{tcs}.
%
\begin{table*}[!ht]    
  \scriptsize
  \centering
        \caption{Averaged Results, Each Test} \label{tab:results}   
       \begin{tabular}{c c c c c c c c c}
         \toprule
         Cores & TS Elements & \multicolumn{4}{c}{Calculation Time ($\si{\second}$)} & \multicolumn{3}{c}{Accuracy Difference ($\si{\mega\pascal}$)} \\ 
         & $\times 10^6$ & CS & CD & FD & AD & CS & CD & FD \\
        \midrule
        1 & $\num{1.99}$  & 3.5 & 2.7 & 1.7 & 1.6 & $\num{1.92E-10}$ & $\num{1.21E-4}$ & .137 \\
        1 & $\num{4.25}$  & 6.2& 4.9& 3.2& 2.9 & $\num{2.28E-10}$& $\num{9.94E-4}$ & .148 \\
        1 & $\num{7.79}$  & 11.2& 8.9& 5.7& 5.2 & $\num{2.38E-10}$& $\num{1.59E-4}$ & .145\\
        1 & $\num{15.4}$  & 26.7& 21.0& 13.4& 12.2 & $\num{2.33E-10}$ & $\num{4.61E-4}$ & .12 \\
        1 & $\num{20.0}$  & 28.1& 22.2& 14.4& 13.1 & $\num{2.76E-10}$ & $\num{1.05E-3}$ & .145 \\
        1 & $\num{31.4}$  & 47.6& 37.7& 24.2& 21.9 & $\num{2.64E-10}$ & $\num{1.65E-3}$ & .133 \\
        1 & $\num{40.1}$  & 55.6& 44.1& 28.4& 25.9 & $\num{3.03E-10}$ & $\num{1.92E-3}$ & .148 \\
        1 & $\num{83.9}$  & 138.9& 109.6& 70.2& 64.0 & $\num{3.63E-10}$ & $\num{1.64E-3}$ & .123 \\
        1 & $\num{165.0}$  & 277.3& 218.1& 139.4& 126.5 & $\num{3.26E-10}$ & $\num{2.18E-3}$ & .128 \\
        32 & $\num{1670}$  & 336.1& 277.7& 200.6& 233.1 & $\num{6.21E-10}$ & $\num{1.52E-2}$ & .176 \\
        64 & $\num{1670}$  & 169.9& 140.7& 102.0& 119.7 & $\num{6.20E-10}$ & $\num{1.50E-2}$ & .177 \\
        96 & $\num{1670}$  & 114.7& 95.0& 69.1 & 79.7 & $\num{6.18E-10}$ & $\num{1.50E-2}$ & .177 \\
        128 & $\num{1670}$  & 86.4& 71.8& 52.4 &58.8 & $\num{6.16E-10}$ & $\num{1.47E-2}$ & .177 \\
        \bottomrule
    \end{tabular}
\end{table*}

@@

\section{Conclusions}
\label{sec:Conc}
%
\subsection{For further studies of Jacobian accuracy in Newton's method}
\label{subsec:FurtherStudies}
The question is raised; what is the significance of Jacobian estimation
accuracy to the convergence of Newton's method?  The per-iteration and even
convergence studies shown here indicate the effect of Jacobian accuracy for
only a single datum, a very accurate Jacobian estimate, while the validation
problem indicates the effect of using a grossly inaccurate Jacobian. The results here show that
for very small Jacobian estimate inaccuracies, convergence rate is not
affected, while for grossly inaccurate Jacobians Newton's method fails. 
Additional confounding factors include that a Jacobian is only first
order approximation of an often curved energy surface and that a non-naive implementation of Newton's
method includes a line search phase that helps in choosing an optimal iterate given a Jacobian.
Is it worthwhile then to investigate the effect of using moderately inaccurate Jacobians, 
produced deliberately or otherwise, on the convergence rate of Newton's method?
